---
title: "Testing Hooks"
author: "Peter von Rohr"
date: "30 Januar 2017"
output: pdf_document
---

# Three arguments in chunk hooks

A chunk hook has three arguments: `before`, `options` and `envir`. We show how they work through some simple examples.

## The `before` argument

It is a logical argument: `before == TRUE` executes code before a chunk.

```{r}
library(knitr)
knit_hooks$set(foo1 = function(before, options, envir) {
  if (before) {
    '_I appear before a chunk!_\n\n'
  } else {
    '\n\n_I am after a chunk..._'
  }
})
```

Test the `foo1` hook:

```{r foo1='whatever'}
1+1
```

## The `options` argument

It contains all the chunk options (include global options) for the current chunk.

```{r}
knit_hooks$set(foo2 = function(before, options, envir) {
  if (!before) {
    z = capture.output(str(options[c('eval', 'dev', 'results', 'bar1', 'bar2', 'bar3','label')]))
    z = paste('    ', z, sep = '', collapse = '\n')
    paste('Some chunk options in the above chunk are:\n\n', z, sep = '')
  }
})
```

Test the `foo2` hook:

```{r SpecialFooChunk, foo2='hi', bar1=TRUE, bar2='asdf', bar3=3.14159}
1+1
```

## The `envir` argument

It is the environment of the current chunk.

```{r}
knit_hooks$set(foo3 = function(before, options, envir) {
  if (!before) {
    paste('Objects available in the above chunk:',
          paste('`', ls(envir), '`', sep = '', collapse = ', '))
  }
})
```

Test the `foo3` hook:

```{r foo3=TRUE}
x2=1+1; y3=rnorm(10)
```

Another example:

```{r}
knit_hooks$set(foo4 = function(before, options, envir) {
  if (!before && exists('z5', envir = envir)) {
    sprintf('**Ha! I see z5 = %.3f!**', envir$z5)
  }
})
```

Test `foo4`:

```{r foo4='qwer'}
pi
```

This above chunk is quiet because `z5` does not exist yet.

```{r foo4='asdf'}
z5=2*pi
```


## Own example
We want to use chunk-hooks to convert graphics from a given format, like LibreOffice-Draw into pdf or png which can be included in documents. 

```{r, results='hide'}
knit_hooks$set(conv.odg = function(before, options, envir) {
  if (is.null(options$label))
    stop(" *** ERROR: chunk must be labelled\n")
  if (is.null(options$odg.path)){
    odg.path <- "odg"
  } else {
    odg.path <- options$odg.path
  }
  odg.fname <- paste(options$label, "odg", sep = ".")
  odg.fig.src  <- file.path(odg.path, odg.fname)
  trg.fig <- paste(options$label, "pdf", sep = ".")
  if (before) {
    if (!file.exists(odg.fig.src))
      rmddochelper::create_odg_graphic(psGraphicName = odg.fname, psGraphicPath = odg.path)
    if (!file.exists(trg.fig) | !options$odg.graph.cache)
      rmddochelper:::convertLibOToGraphic(psLibOFile = odg.fname, psOutFormat = "pdf", psLibODir = odg.path)
  }
})
```

Now we create a chunk that includes a figure

```{r FigInclude, conv.odg=TRUE, odg.path="odg", odg.graph.cache=FALSE}
knitr::include_graphics(path = "FigInclude.pdf")
```

This is the first line after the figure inclusion.

```{r}
Sys.time()
sessionInfo()
```

